Dark matter halo concentrations with a bayesian approach

### 2014-09-23 paper/article.tex
new lines

>>>>

Running another test with halos whose concentrations vary as a normal distribution of variance ${\sigma}^2$ we found that the concentrations obtained by the method of circular velocity are a 35\% greater than the ones obtained by the density method. However the concentrations obtained by the velocity method are barey higher (around 2\% or 3\%) than the ones obtained by our method. We did not find any significant variation in the concentration values obtained by any method by changing ${\sigma}^2$ in contrast with FIXME.
